Brownian Dynein Model

### 2015-07-25 latex/derivation.tex
Expand solutions on final page to include only angular velocity terms. The solutions now look really bad and don't seem to be solvable. New approach time?

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br}
\end{align}

@@

\section{System after Addition}
By adding coordinates for br to mr, mr to t, and t to ml, we simplify one side of our equations. \\

@@

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
{{L_{t}}^2}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
{{L_{t}}^2}
\end{equation}

\begin{equation}
\dot{\Theta}_{br} =
\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
+ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{equation}

@@

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

@@

\begin{equation}
\dot{\Theta}_{br} =
\frac{1}{L_{t}}\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi)
+ \frac{1}{L_{t}}\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{equation}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

\begin{multline}
\dot{\Theta}_{bl} =
\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

>>>>

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
\end{align}

@@

\section{System after Addition}
By adding equations from our system together we can isolate the $\lambda$ values. \\

@@

\begin{equation}
\dot{\Theta}_{br} =
\frac{\Big(\dot{Y}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)(L_{t}\cos(\Theta_{br}-\pi))}
{{L_{t}}^2}
+ \frac{\Big(\dot{X}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)(L_{t}\sin(\Theta_{br}-\pi))}
{{L_{t}}^2}
\end{equation}
\\
Now expand the cartesian velocity definition: \\

\begin{multline}
\dot{\Theta}_{br} =
\frac{1}{L_{t}}\Big(\mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
+ \frac{1}{L_{t}}\Big(L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(\dot{X}_{br} + \dot{X}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}
\\
Now expand the cartesian velocity definition: \\

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\mn 2L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(2L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{Y}_{br} + \dot{Y}_{ml}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
\\
Now expand the cartesian velocity definition: \\

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
\\
Now expand the cartesian velocity definition: \\

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

@@

\begin{multline}
\dot{\Theta}_{br} =
\frac{1}{L_{t}}\Big(\mn L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{ybr} - R_{ybr} \Big)\cos(\Theta_{br}-\pi) \\
+ \frac{1}{L_{t}}\Big(L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} - \frac{1}{\gamma}F_{xbr} - R_{xbr} \Big)\sin(\Theta_{br}-\pi)
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\mn 2L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 2L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
  - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(2L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
   - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\mn3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + 2\mn L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + 2\mn L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 2L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\mn 3L_{t}\cos(\Theta_{bl})\dot{\Theta}_{bl} + \mn 3L_{s}\cos(\Theta_{ml})\dot{\Theta}_{ml} + \mn 2L_{s}\cos(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + \mn L_{t}\cos(\Theta_{br}-\pi)\dot{\Theta}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(3L_{t}\sin(\Theta_{bl})\dot{\Theta}_{bl} + 3L_{s}\sin(\Theta_{ml})\dot{\Theta}_{ml} + 2L_{s}\sin(\Theta_{mr}-\pi)\dot{\Theta}_{mr} + L_{t}\sin(\Theta_{br}-\pi)\dot{\Theta}_{br} 
- \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
